Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-07-17 MSc-dissertation.tex
New para

\subsubsection{Adaptive functiosn and factors}

@@

@@

@@

>>>>

\subsubsection{Adaptive functions and factors}

@@

SMC can be more adaptive by introducing adaptive distance function and adaptive population; besides, factors can be applied to manually `normalise' the data.

The trivial distance function is set to Euclidean distance (2-norm distance)

\begin{align}
    \label{eq:dis}
    D=\sqrt{\sum_i \Delta x_i^2}
\end{align}

where $i$ is the index of data points and $\Delta x_i$ is the discrepancy between  observed data and simulated data at data point $i$, i.e. $\Delta x_i = x_{i, simulated}-x_{i, observed}$. In this case data points are 12 time points of four variables i.e. 48 data points in total.

A weighted 2-norm distance can be written as

\begin{align}
    \label{dis_w}
    D=\sqrt{\sum_i w_i \Delta x_i^2}
\end{align}

where a weight $w_i$ is assigned to every data point. If data point $i$ have a higher weight, then the data value is regeared to be more informative, i.e. giving more help in inferring the true posteriors; weights can be either pre-set according to prior knowledge of the problem, or using adaptive method to be dynamically calculated according to , known as adaptive distance.

Adaptive distance is changing the weights of all data points after each generation iteration, trying to assign informative data points higher weights. Additionally, implementation of adaptive in \verb|pyABC| also introduces additional factors $f_i$ multiplied to weights \cite{ref:adpt_dis}

\begin{align}
    \label{dis_w}
    D=\sqrt{\sum_i f_iw_i \Delta x_i^2}
\end{align}

Factor is helpful as an option for efficiency. When some data points are equally informative, the manually pre-defined can make the distance more focused on certain data point, or behave like a normalisation that can balance the scales of different summarised statistics (here is the 48 mean values). There are two appliance case studied: (1) factors used as an normalisation option ans (2) factors used to give more focus on some features of the observed data. For (2), as we noticed that the main features (e.g. rapid increase, peaks, fluctuations) are mostly observed in the first half of the time points i.e. 0 - 30 hpl, factors are tried in the later parameter estimation of real data where a more accurate fit of the curve is desired.

Adaptive population \cite{ref:adpt_pop} can adapt the population size of each generation according to the mean correlation of variation error of the previous population. In our early test the maximal population size that is allowed is set to 5,000 and the adaptive strategy always select the upper bound, as a results of wide parameter space or the wide posterior approximation shape.

@@

[picture here]

[what is the result]

@@

\bibitem{ref:adpt_dis} Prangle, D., 2017. Adapting the ABC distance function. Bayesian Analysis, 12(1), pp.289-309.

\bibitem{ref:adpt_pop} Klinger, E. and Hasenauer, J., 2017, September. A scheme for adaptive selection of population sizes in approximate Bayesian computation-sequential Monte Carlo. In International Conference on Computational Methods in Systems Biology (pp. 128-144). Springer, Cham.

### 2020-07-17 __latexindent_temp.tex
New para

\usepackage{epcc}
\usepackage{graphics}
\usepackage{mathtools}

@@

\begin{center}
\resizebox{1.0\hsize}{!}{\includegraphics{fig/obs_curve.png}}
\end{center}

\caption{Mean of the observed data for neutrophil $N$, macrophage $\Phi$, il-1$\beta$ and tnf-$\alpha$, from experiment results of \cite{ref:Tsarouchas}. Error bars indicate standard error of mean} 
\label{fig:obs_data}

@@

A preliminary model is proposed according to \cite{ref:Tsarouchas} and used to build and test the code.

\begin{equation*}\label{eq:pareto mle2}
    \begin{multlined}
        \frac{\mathrm{d} N}{\mathrm{d} t}=\lambda_N+\kappa_{N\beta}\beta-\mu_NN-\nu_{N\Phi}N\Phi\\
\frac{\mathrm{d} \Phi}{\mathrm{d} t}=\lambda_\Phi+\kappa_{\Phi\beta}\beta-\mu_\Phi\Phi\\
\frac{\mathrm{d} \beta}{\mathrm{d} t}=\frac{s_{\beta N}N}{1+i_{\beta\Phi}\Phi}-\mu_\beta\beta\\
\frac{\mathrm{d} \alpha}{\mathrm{d} t}=s_{\alpha\Phi}\Phi-\mu_\alpha\alpha
   \end{multlined}
  \end{equation*}

@@

@@

\section{Parameter estimation}
Here are some results.

\section{Model comparison}
Here are some results.

@@

\chapter{Results Analysis}

@@

\section{Discussions}
This is the place to put your conclusions about your work. You can
split it into different sections if appropriate. You may want to include
a section of future work which could be carried out to continue your
research.

@@

\chapter{Stuff which is too detailed}

Appendices should contain all the material which is considered too
detailed to be included in the main bod but which is, nevertheless,
important enough to be included in the thesis.

\chapter{Stuff which no-one will read}

Some people include in their thesis a lot of detail, particularly
computer code, which no-one will ever read. You should be careful that
anything like this you include should contain some element of uniqueness
which justifies its inclusion.

@@

\bibitem{ref:Tsarouchas} Tsarouchas, T.M., Wehner, D., Cavone, L., Munir, T., Keatinge, M., Lambertus, M., Underhill, A., Barrett, T., Kassapis, E., Ogryzko, N. and Feng, Y., 2018. Dynamic control of proinflam- matory cytokines Il-1$\beta$ and Tnf-$\alpha$ by macrophages in zebrafish spinal cord regeneration. Nature communications, 9(1), pp.1-17.

>>>>

\usepackage{epcc}
\usepackage{graphics}
% \usepackage{mathtools}
\usepackage{amsmath}

@@

\begin{figure}
\begin{center}
\resizebox{1.0\hsize}{!}{\includegraphics{fig/obs_curve.png}}
\end{center}

\caption[Mean of the observed data]%
{Mean of the observed data for neutrophil $N$, macrophage $\Phi$, il-1$\beta$ and tnf-$\alpha$, from experiment results of \cite{ref:Tsarouchas}. Error bars indicate standard error of mean} 
\label{fig:obs_data}

@@

A preliminary model is proposed according to \cite{ref:Tsarouchas} and used to build and test the code. A interaction map illustrate the model is shown in Figure \ref{fig:m1}. This model is a simplification a the process described in \cite{ref:Tsarouchas}. To describe the parameters' units, we denote the unit of $N$ and $\Phi$ i.e. number of cells as `cell', and denote the unit of $\beta$ and $\aleph$ i.e. relative mRNA expression as `unit' for simplicity.

\begin{figure}
    \begin{center}
    \resizebox{0.4\hsize}{!}{\includegraphics{fig/model1.png}}
    \end{center}

    \caption[Interactions modelled in the basic model]%
    {Interactions modelled in the basic model (model 1) based on Tsarouchas et al.\cite{ref:Tsarouchas}. Lines ended with arrow represent promoting effect, lines ended with T-connectors represent inhibition} 
    \label{fig:m1}

It is assumed that there are negative feedbacks for all the variables. MORE DESCRIBE.

\begin{align}
    \label{eq:model1}
    \begin{split}
        &\frac{\mathrm{d} N}{\mathrm{d} t}=\lambda_N+\kappa_{N\beta}\beta-\mu_NN-\nu_{N\Phi}N\Phi\\
        &\frac{\mathrm{d} \Phi}{\mathrm{d} t}=\lambda_\Phi+\kappa_{\Phi\beta}\beta-\mu_\Phi\Phi\\
        &\frac{\mathrm{d} \beta}{\mathrm{d} t}=\frac{s_{\beta N}N}{1+i_{\beta\Phi}\Phi}-\mu_\beta\beta\\
        &\frac{\mathrm{d} \alpha}{\mathrm{d} t}=s_{\alpha\Phi}\Phi-\mu_\alpha\alpha
    \end{split}
\end{align}

\begin{table}[h!]
\centering
\begin{tabular}{|c c c|} 
 \hline
 Parameter & Definition & Units\\ [0.5ex] 
 \hline\hline
 $\lambda_N$ & Self-increase rate of neutrophil & $cell/h$  \\ 
 $\kappa_{N\beta}$ & Promoting effect coefficient by il-1$\beta$ & $cell/(unit\cdotp h)$\\
 $\mu_N$ & Coefficient of negative feedback of $N$ & $h^{-1}$ \\
 $\nu_{N\Phi}$ & Coefficient of inhibition of both $N$ and $\Phi$& $cell^{-1}\cdotp h^{-1}$ \\
 \hline
 $\lambda_\Phi$ & Self-increase rate of macrophage & $cell/h$ \\
 $\kappa_{\Phi\beta}$ & Promoting effect coefficient by il-1$\beta$ & $cell/(unit\cdotp h)$ \\
 $\mu_\Phi$ &  Coefficient of negative feedback of $\Phi$ & $h^{-1}$ \\
 \hline
 $s_{\beta N}$ & Production rate from $N$ & $unit/(cell\cdotp h)$ \\
 $i_{\beta\Phi}$ & Coefficient of inhibition to the production & $cell^{-1}$ \\
 $\mu_\beta$ & Coefficient of negative feedback of $\beta$ & $h^{-1}$ \\
 \hline
 $s_{\alpha\Phi}$ & Production rate from $\Phi$ & $unit/(cell\cdotp h)$ \\
 $\mu_\alpha$ & Coefficient of negative feedback of $\alpha$ & $h^{-1}$ \\
[1ex] 
 \hline
\end{tabular}
\caption{Parameters introduced in the basic model (model 1)}
\label{table:m1}
\end{table}

@@

[feasible or not; goodness of fit; features of these models]

[bayes factor for model selection]

\subsection{Limitations}

[hypothesis]

[available data]

[model misspecification]

@@

This chapter focuses on the implementation of the ABC SMC on the proposed models. Estimation of  parameters in the proposed models is the main task of this section. ABC SMC-based models selection is another task that can be easily implemented with the parameter estimation framework.

The build and test is under \verb|Python| environment with \verb|pyABC|\cite{ref:pyabc}. Some other code e.g. shell script and \verb|R| code are also used to perform the experiments and analyse the results. Tested software and system environment can be found at Appendix A. The build and test is performed on local computers and HPC clusters available within EPCC.

\section{Parameter estimation}

[implementation details and options/ settings that are affecting the ABC]

As the key focus of this project is on the parameter estimations of dynamical system, the ability of inference on the proposed model is firstly examined before actual inference using the experimental observed data.

In the first part, synthetic data is used with known true parameter values. The algorithm implementation is evaluated by the efficiency and goodness of resultant model under different implementation options and ABC SMC hyperparameters.

Then according to findings in the first part, several options with good performance are tried in the inference using experimental observed data (Figure \ref{fig:obs_data}). To obtain a more accurate and general results, these experiments are repeated for 3 or more times.

\subsection{ABC SMC and model hyperparameters experiments}

[including the options that are tested/ tried/ not adopted]

[including experiments results and discussions]

[how do these options correspond to biological model and how to set them accordingly for proposed model]

The ABC SMC inference can have largely different performance when using different hyperparameters and implementation options. To firstly test the ability of inference and observe the results of different options, synthetic data with known true parameter values are used as target data. The true value of parameters that are used to generate synthetic data is listed in Appendix B.1. These true values are firstly obtained by fitting a least square fit of model 1 onto the experimental data (Figure \ref{fig:infer_back_data}), the target data is then generated using these parameter values via ODE solver in \verb|Python|.

\begin{figure}
    \begin{center}
    \resizebox{1.0\hsize}{!}{\includegraphics{fig/LS.png}}
    \end{center}

    \caption[Synthetic data generated with known parameter values]%
    {Synthetic data generated with known parameter values (line plot), compared to experimental data (scatter plot)} 
    \label{fig:infer_back_data}

Among them the following topics are studied using synthetic data.

\subsubsection{Perturbation kernels}

Perturbation kernels work in the sampling process. In each generation $t$, samples are firstly taken from the previous population $\{\theta_{t-1}\}$ with weights $\{w_{t-1}\}$, then perturbed using the perturbation kernel $K(\theta|\theta^*)$. We keep sampling until $N$ particles are accepted, where $N$ is the pre-set population size. After that the new weights are calculated and normalised.

\begin{figure}
    \begin{center}
    \resizebox{1.0\hsize}{!}{\includegraphics{fig/smc.png}}
    \end{center}

    \caption{ABC SMC sampling process} 
    \label{fig:smc}

The perturbation kernel is called in the sampling of every particles and determines how the new perturbed particle is chosen, thus it is influential to both computation complexity and the resultant posterior distribution. Generally, a local perturbation kernel may face the risk of being stuck in local modes (e,g., local optimal), but it may need less computational operations, or could generate a population with a higher acceptance rate if the successive epsilon values are close; A kernel with wide variance, or spreading out in a large space could help in resolving the local optimal problem by a more thoroughly exploration of the parameter space, however it can be more computation-intensive and result in a lower acceptance rate. A desired optimal kernel should balance the trade-offs; their property and criteria is discussed in \cite{ref:kernel}.

There are several common choice of perturbation kernels. Among them multivariate normal kernel and local M-nearest neighbour model is preferred to be applied on our models. A covariance matrix $\Sigma_t$ of accepted particles is calculated form previous generation and used in multivariate normal kernel: $K(\theta|\theta_{t-1})\sim\mathcal{N}(\theta_{t-1}, \Sigma_t)$. It is illustrated to be more efficient than uniform kernel and component-wise normal kernel in relecting the true posterior structure \cite{ref:kernel}. It has been proved to perform well in several dynamic system models \cite{ref:abcsysbio, ref:compare, ref:disease} for the parameter estimation and model selection tasks. The $scaling\in(0,1]$ parameter in \verb|pyABC| will be multiplied to the covariance to produce a `narrower distributed' perturbation result.

Local M-NN kernel provided by \verb|pyABC| is also tried to provide a comparison. A local kernel density estimation (KDE) fit is used with M nearest neighbours considered.

The kernel experiments is designed to explore the efficiency of SMC on our dynamical systems. Given the same fixed threshold schedule, kernels that need less total samples and have higher acceptance rate would be our preference. The experiments compared multivariate normal kernel with local MNN kernels with different parameters, using synthetic data to infer back the parameters. The acceptance rate among each time point and total required samples are compared after the experiment to give suggestions on the kernel selection in the real data inference. As the threshold schedule is fixed, the final population should have similar discrepancy to the target data thus here the goodness of fit i.e. recover of target data trends/features and errors of the inferred parameters compared to true values is not discussed.

\subsubsection{Kernel experiment results}

To compare kernels, a fixed schedule schedule is used with minimal epsilon i.e. $\epsilon_t$ set to 10.0. From the total required samples graph Figure \ref{fig:kernel1}, the efficiency can be compared. Among the tested kernels, the local M-NN with M=50 has the best performance: it requires the least number of samples and 
has higher acceptance rates among almost all generations. Local M-NN with M=750 is the slowest kernel.

For local M-NN kernels, generally a greater M will lead to lower acceptance rate and 
more required particles in each generation. As shown in Figure \ref{fig:acceptance1}, local M-NN with M=750 is the lowest curve. Consequently, if greater M is test, then it will have even lower acceptance rates; the maximum M=2000 (whole population is considered) will have the lowest acceptance rates.

\begin{figure}
    \begin{center}
    \resizebox{1.0\hsize}{!}{\includegraphics{fig/kernel1.png}}
    \end{center}

    \caption[Total required samples of different kernels]%
        {Total required samples of different kernels. Different color represents different generations (bottom to top: generation 1 to generation 20)}
    \label{fig:kernel1}

    \vspace*{\floatsep}

    \begin{center}
    \resizebox{1.0\hsize}{!}{\includegraphics{fig/acceptance1.png}}
    \end{center}

    \caption{Acceptance rates of different kernels}
    \label{fig:acceptance1}

Multivariate normal kernel has a performance between local M-NN M=250 and M=100. It proves that rather than a trivial normal kernel, multivariate normal kernels is more efficient facing the concentrations of joint distributions among multiple parameters \cite{ref:kernel}. `Scaling' option can narrower the distribution calculated from the last population, thus making the kernel more `local' by sampling under a smaller variance. Similar to small M in local M-NN, small `scaling' is also more efficient in our experiment of the model 1. Besides the fixed threshold schedule, a median threshold schedule with the same final threshold $\epsilon_{20}=10.0$ is also tested and similar results are observed (Figure \ref{fig:kernel2} and \ref{fig:acceptance2}, Appendix B2).

It seems that a more `local' kernel can give better performance by efficiently sampling around concentrations in parameters' distribution and approximate the posterior distribution. This holds in most cases under a given target final threshold value $\epsilon_t$, however may not produce the proper result want: a more local kernel, e.g. local M-NN with small M and multivariate normal with `scaling' is more likely to be stuck in local optimality, as the kernel is less likely to sample particles that are far from local concentrations, although these local optimal are still accepted under given threshold. In other words, using local kernels the epsilon may quickly converge to to local optimal; if a even smaller epsilon is desired, the local kernel can hardly generate enough particles to find another matched local modes. Also, the shapes of posterior distribution will affect the performance of local kernels \cite{ref:kernel}. One obvious example is presented in Figure \ref{fig:kernel1}, where local M-NN with M=50 suffered from a local optimal: the last generation takes much more samples to meet the required threshold.

\paragraph{Conclusion} Local kernels can be fast bur unstable in some case; for a general parameter inference of our models, multivariate kernels are preferred, as a good fit is our prior target; some local kernels are also worth trying after the multivariate normal kernel, e.g. local M-NN with M$\leq 250$ (for population size of 2000, i.e. 12.5\% of the population) and multivariate normal with scaling. Also multivariate M-NN is worth trying, although it is not built in \verb|pyABC| and requires additional implementations.

% \begin{figure}
%     \begin{center}
%     \resizebox{1.0\hsize}{!}{\includegraphics{fig/acceptance1.png}}
%     \end{center}

%     \caption{Acceptance rates of different kernels}
%     \label{fig:acceptance1}

\subsubsection{Adaptive functions and factors}

[how adaptive distance work]

SMC can be more adaptive by introducing adaptive distance function and adaptive population; besides, factors can be applied to manually `normalise' the data.

The trivial distance function is set to Euclidean distance (2-norm distance)

\begin{align}
    \label{eq:dis}
    D=\sqrt{\sum_i \Delta x_i^2}
\end{align}

where $i$ is the index of data points and $\Delta x_i$ is the discrepancy between  observed data and simulated data at data point $i$, i.e. $\Delta x_i = x_{i, simulated}-x_{i, observed}$. In this case data points are 12 time points of four variables i.e. 48 data points in total.

A weighted 2-norm distance can be written as

\begin{align}
    \label{dis_w}
    D=\sqrt{\sum_i w_i \Delta x_i^2}
\end{align}

where a weight $w_i$ is assigned to every data point. If data point $i$ have a higher weight, then the data value is regeared to be more informative, i.e. giving more help in inferring the true posteriors; weights can be either pre-set according to prior knowledge of the problem, or using adaptive method to be dynamically calculated according to , known as adaptive distance.

Adaptive distance is changing the weights of all data points after each generation iteration, trying to assign informative data points higher weights. Additionally, implementation of adaptive in \verb|pyABC| also introduces additional factors $f_i$ multiplied to weights \cite{ref:adpt_dis}

\begin{align}
    \label{dis_w}
    D=\sqrt{\sum_i f_iw_i \Delta x_i^2}
\end{align}

Factor is helpful as an option for efficiency. When some data points are equally informative, the manually pre-defined can make the distance more focused on certain data point, or behave like a normalisation that can balance the scales of different summarised statistics (here is the 48 mean values). There are two appliance case studied: (1) factors used as an normalisation option ans (2) factors used to give more focus on some features of the observed data. For (2), as we noticed that the main features (e.g. rapid increase, peaks, fluctuations) are mostly observed in the first half of the time points i.e. 0 - 30 hpl, factors are tried in the later parameter estimation of real data where a more accurate fit of the curve is desired.

Adaptive population \cite{ref:adpt_pop} can adapt the population size of each generation according to the

[what is factor]

[what is adaptive distance]

\subsubsection{Experiments results}

\paragraph{Conclusion}

\subsubsection{Data size, prior range, population size and generations}

[experiments plan]

\subsubsection{Experiments results}

\paragraph{Conclusion}

\subsection{Implementations and code}

[ABC implementations details, e.g. distance, population, ODE related functions]

[how the code is developed and built]

\section{Model comparison}

[comparison of model 1, 2 and 3]

[further comparison of model 3, 4 and 5]

@@

\chapter{Results and Discussions}

[WHAT results is outputted and WHAT topics are discussed]

@@

[scaling-up performance: speed-up and efficiency]

[profiling results: hot-spot and possible improvements]

\section{Discussions}

[goodness of fit (evaluation); preferred models and effects of modification to basic model]

[efficiency and trade-offs in scaling-up]

[POSSIBLE: compare to exact inference; compared to other implementations]

[limitations]

@@

\chapter{System and software environment}

\section{ABC SMC implementation}

\section{Data analysis}

\chapter{Data and settings}

\section{Infer-back experiments}

\subsection{Parameter values used to generate synthetic data}

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c c|} 
     \hline
     Parameter & Value & Unit\\ [0.5ex] 
     \hline\hline
     $\lambda_N$ & 2.1989 & $cell/h$  \\ 
     $\kappa_{N\beta}$ & 3.9627 & $cell/(unit\cdotp h)$\\
     $\mu_N$ & 1.7219 & $h^{-1}$\\
     $\nu_{N\Phi}$ & 0.2195 & $cell^{-1}\cdotp h^{-1}$ \\
     \hline
     $\lambda_\Phi$ & 1.3146 & $cell/h$ \\
     $\kappa_{\Phi\beta}$ & 0.1235 & $cell/(unit\cdotp h)$ \\
     $\mu_\Phi$ & 0.1454 & $h^{-1}$ \\
     \hline
     $s_{\beta N}$ & 6.5536 & $unit/(cell\cdotp h)$ \\
     $i_{\beta\Phi}$ & 1.7062 & $cell^{-1}$ \\
     $\mu_\beta$ & 0.5212 & $h^{-1}$ \\
     \hline
     $s_{\alpha\Phi}$ & 10.2416 & $unit/(cell\cdotp h)$ \\
     $\mu_\alpha$ & 19.6642 & $h^{-1}$ \\
    [1ex] 
     \hline
    \end{tabular}
    \caption{Parameter values}
    \label{table:m1}
\end{table}

\section{Kernel experiment: median epsilon schedule}

    \begin{center}
    \resizebox{1.0\hsize}{!}{\includegraphics{fig/kernel2.png}}
    \end{center}

    \caption{Total sampling size} 
    \label{fig:kernel2}

    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/acceptance2.png}}
        \end{center}

        \caption{Acceptance rates} 
        \label{fig:acceptance2}

@@

\bibitem{ref:Tsarouchas} Tsarouchas, T.M., Wehner, D., Cavone, L., Munir, T., Keatinge, M., Lambertus, M., Underhill, A., Barrett, T., Kassapis, E., Ogryzko, N. and Feng, Y., 2018. Dynamic control of proinflammatory cytokines Il-1$\beta$ and Tnf-$\alpha$ by macrophages in zebrafish spinal cord regeneration. Nature communications, 9(1), pp.1-17.

\bibitem{ref:pyabc} Klinger, E., Rickert, D. and Hasenauer, J., 2018. pyABC: distributed, likelihood-free inference. Bioinformatics, 34(20), pp.3591-3593.

\bibitem{ref:kernel} Filippi, S., Barnes, C. P., Cornebise, J., and Stumpf, M..H. (2013). On optimality of kernels for approximate Bayesian computation using sequential Monte Carlo. Statistical Applications in Genetics and Molecular Biology 12, 1, 87-107.

\bibitem{ref:abcsysbio} Liepe, J., Kirk, P., Filippi, S., Toni, T., Barnes, C.P., and Stumpf, M.P.H., 2014. A framework for parameter estimation and model selection from experimental data in systems biology using approximate Bayesian computation. Nature Protocols. 9 (2) pp. 439–456.

\bibitem{ref:compare} Daly AC, Cooper J, GavaghanDJ, Holmes C. 2017. Comparing two sequentialMonte Carlo samplers for exact andapproximate Bayesian inference on biologicalmodels.J. R. Soc. Interface14: 20170340.

\bibitem{ref:disease} Minter, A. and Retkute, R., 2019. Approximate Bayesian Computation for infectious disease modelling. Epidemics, 29, p.100368.

\bibitem{ref:adpt_dis} Prangle, D., 2017. Adapting the ABC distance function. Bayesian Analysis, 12(1), pp.289-309.

\bibitem{ref:adpt_pop} Klinger, E. and Hasenauer, J., 2017, September. A scheme for adaptive selection of population sizes in approximate Bayesian computation-sequential Monte Carlo. In International Conference on Computational Methods in Systems Biology (pp. 128-144). Springer, Cham.
